\SdM{Gaia identifies VFTS682 as the most massive, dynamically ejected runaway star known to date}

### 2018-05-11 VFTS682.tex
converted to apjletters

%Selma's comments
\definecolor{Wildstrawberry}{rgb}{1.0, 0.26, 0.64}
\newcommand{\SdM}[1]{{{\color{Wildstrawberry}\bf{#1}}}}
\newcommand{\newtext}[1]{{\color{ForestGreen}\bf{#1}}}

@@

\thanks{M.~Renzo, \href{mailto:m.renzo@uva.nl}{m.renzo@uva.nl}}
\date{}
\begin{abstract}
...\\
\SdM{Mathieu: please use emulate apj template for this.  We would be submitting there. }...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
\end{abstract}

@@

How do massive stars form is one of the major longstanding questions in astrophysics
\citep[e.g.,][]{zinnecker:07}. Obtaining clues from observations has been challenging, because massive stars are intrinsically rare, 
%\citep[e.g.,][]{salpeter:55,kroupa:01, schneider:18}, 
evolve fast, typically reside in dense groups and they remain enshrouded in their parent cloud during the formation
process.  Major progress has been made on the theoretical side,  \citep[e.g.][]{Kuiper+2015,Rosen+2016}, but the simulations are computationally very expensive. They can typically not yet resolve the length scales that are of interest to understand the 
high level of multiplicity among massive stars  \citep[][]{sana:12,sana:17}.  Understanding massive star formation, and its possible dependence on environment and metallicity, is crucial for understanding the role massive stars play within their host galaxies as sources of feedback, but also for understanding the transients that mark their death and the compact remnants they leave behind.  This is therefore a key question for the present and upcoming transient surveys \citep[e.g., LSST, BlackGem, LIGO/Virgo O3][]{}\todo{ref} which  will reveal transients associated to massive stars
evolution and death.

>>>>

%Selma's comments
\definecolor{Wildstrawberry}{rgb}{1.0, 0.26, 0.64}
\newcommand{\SdM}[1]{{{\color{Wildstrawberry}{#1}}}}
\newcommand{\newtext}[1]{{\color{ForestGreen}\bf{#1}}}

@@

\thanks{M.~Renzo, \href{mailto:m.renzo@uva.nl}{m.renzo@uva.nl}}
\date{}
\begin{abstract}
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
\end{abstract}

@@

How do massive stars form is one of the major longstanding questions in astrophysics
\citep[e.g.,][]{zinnecker:07}. Obtaining clues from observations has been challenging, because massive stars are intrinsically rare, 
%\citep[e.g.,][]{salpeter:55,kroupa:01, schneider:18}, 
evolve fast, typically reside in dense groups and they remain enshrouded in their parent cloud during the formation
process.  Major progress has been made on the theoretical side,  \citep[e.g.][]{Kuiper+2015,Rosen+2016}, but the simulations are computationally very expensive. They can typically not yet resolve the length scales that are of interest to understand the 
high level of multiplicity among massive stars  \citep[][]{sana:12,sana:17}.  Understanding massive star formation, and its possible dependence on environment and metallicity, is crucial for understanding the role massive stars play within their host galaxies as sources of feedback, but also for understanding the transients that mark their death and the compact remnants they leave behind.  This is therefore a key question for the present and upcoming transient surveys e.g., LSST and LIGO/Virgo,
%\citep[][]{}\todo{ref} . Blackgem is still hypothetical and a very tiny project compared to the others.  
which  will reveal transients associated to massive stars
evolution and death.
